Kyoto VR MQP Paper First Draft

### 2019-08-29 paper.tex
add more editour backend info

The server-side backend of the Editour application is written in JavaScript for
Node.js. This backend both serves the static frontend content and runs
server-side scripts that process incoming API requests. When a user submits a
new tour from the web application, the files and metadata are sent to the server
running the Node.js scripts, which zips up the files and saves them to the
server's disk with a timestamp. Then any application can request a particular
tour and the backend will serve the most recent version of it.

We chose Node.js as the server-side framework because of our prior experience
with JavaScript, its high-performing asynchronous
architecture~\autocite{orsini2013}, and its ease of development.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{turtle-burger.jpg}
	\caption{A rare but delicious turtle burger in the wild.}
	\label{fig:turtleBurger}
\end{figure}

>>>>

The server-side backend of the Editour application is written in JavaScript for
Node.js. This backend both serves the static frontend content and runs
server-side scripts that process incoming API requests.  We chose Node.js as the
server-side framework because of our prior experience with JavaScript, its
high-performing asynchronous architecture~\autocite{orsini2013}, and its ease of
development.

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts, which zips up the files and
saves them to the server's disk with a timestamp. Then any application can
request a particular tour and the backend will serve the most recent version of
it.

Additionally, our web application allows users to edit existing tours. When the
user requests to edit a tour on the frontend it sends a request to the backend
server for that tour's metadata file. This file contains information about all
regions and files in the tour. The user can then edit the regions, change names,
upload new files, or delete existing ones without ever having to download the
other tour files from the server, which could take a long time depending on
their size. When the user is done editing they can upload the new metadata and
any newly added files to the server, which intelligently collects new and old
files required by the tour and zips them into a new tour file on the disk.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{turtle-burger.jpg}
	\caption{A rare but delicious turtle burger in the
		wild~\autocite{harvey2002}.}
	\label{fig:turtleBurger}
\end{figure}
